What really matters (and to whom): Investigating heterogeneous effects in high-dimensional conjoint analyses

### 2024-12-20 Manuscript files/Manuscript.qmd
Title page

---
title: "What really matters (and to whom): Investigating heterogeneous effects in high-dimensional conjoint analyses"
author:
  - "Thomas Reiter"
  - "Philipp Sterner"
date: "2024-12-20"
format:
  pdf:
    toc: true
    lof: true
    lot: true
    title-page: true
pdf-engine: xelatex
header-includes:
  - \usepackage{array}
  - \usepackage{ragged2e}
  - \setlength{\extrarowheight}{2pt}
  - \renewcommand{\arraystretch}{1.5}
  - \usepackage{etoolbox}
  - \usepackage{footmisc}
  - \pretocmd{\tableofcontents}{\clearpage\setcounter{page}{2}}{}{}
floatsintext: yes
bibliography: references.bib
editor_options: 
  markdown: 
    wrap: sentence
---

>>>>

---
title: "What really matters (and to whom): Investigating heterogeneous effects in high-dimensional conjoint analyses"

author:
  - name: "Thomas Reiter"
    affiliations: [stat-consulting]
  - name: "Philipp Sterner"
    affiliations: [stat-consulting]

affiliations:
  - id: stat-consulting
    name: "Statistical Consulting, Master Statistics and Data Science, LMU Munich, Institute of Statistics"

abstract: |
  **Supervisor:** Prof. Dr. David Rügamer

  **Project Partners:** Prof. Dr. Paul Thurner and Fabian Haggerty  
  (Geschwister Scholl Institute of Political Science)

date: "2024-12-20"

format:
  pdf:
    toc: true
    lof: true
    lot: true
    title-page: true
    title-block-style: fancy
    # Ensure the order: title, authors, affiliations, abstract, date
    title-block-components: [title, author, affiliations, abstract, date]

pdf-engine: xelatex

header-includes:
  - \usepackage{array}
  - \usepackage{ragged2e}
  - \setlength{\extrarowheight}{2pt}
  - \renewcommand{\arraystretch}{1.5}
  - \usepackage{etoolbox}
  - \usepackage{footmisc}
  - \pretocmd{\tableofcontents}{\clearpage\setcounter{page}{2}}{}{}

floatsintext: yes
bibliography: references.bib
editor_options:
  markdown:
    wrap: sentence
---
